Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Restyle table

\begin{table}[tb]
\begin{center}
\begin{tabular}{cc} \\
flight & matches \\ \hline
0 & (0,6) (2,3) (4,5) \\
1 & (0,2) (4,1) (6,5) \\
2 & (2,1) (0,5) (6,3) \\
3 & (5,1) (0,3) (6,4) \\
4 & (3,5) (6,1) (2,4) \\
5 & (3,1) (0,4) (2,5) \\
6 & (3,4) (6,2) (0,1) \\ \hline
\end{tabular}
\end{center}
\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of
stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of
imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in
position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches
in each position, only achieved by skipper 2.}
\label{tab2}
\end{table}

>>>>

\begin{SCtable}[2.0][tb]
    \setlength{\tabcolsep}{3pt}
    \begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,6) & (2,3) & (4,5) \\
        1 & (0,2) & (4,1) & (6,5) \\
        2 & (2,1) & (0,5) & (6,3) \\
        3 & (5,1) & (0,3) & (6,4) \\
        4 & (3,5) & (6,1) & (2,4) \\
        5 & (3,1) & (0,4) & (2,5) \\
        6 & (3,4) & (6,2) & (0,1) \\ \bottomrule
    \end{tabular}
    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights,
        which is the result of stages 1, 2, and 3. It has 6 boat changes
        and imbalance 1. An example of imbalance is skipper $\sigma[{0}]$
        with 2 matches in position 0 (first), 3 in position 1 and 1 (mid)
        in position 2 (last). Perfect balance would be 2 matches in each
    position, only achieved by skipper 2.}\label{tab2}
\end{SCtable}
